Pool Model - A unified Mathematical\\ Modelling Framework for Food Science

### 2025-10-31 paper/pool_model.tex
move files to base
tex: update figures, change subfigures numeration

% \documentclass[10pt,A4paper]{article}
\documentclass[10pt,twocolumn,5p,authoryear]{elsarticle/elsarticle}
\usepackage[utf8]{inputenc}

@@

\bibliographystyle{elsarticle/elsarticle-harv}

@@

        (a) The time dependence of the total bacterial count $N$ for the model including the back-flow to the lag phase due to temperature stress~(\ref{eq:ode_tempshift_backlag}).
        (b) The value of the corresponding back-flow rate $\gamma$ calculated according to (\ref{eq:gamma_tempshift}).

@@

        The growing bacteria $B$ produces toxin $T_B$ (a) constantly $\dot{T}_B^1 = \mathcal{F}^1 = \kappa G_B$ or (b) only during growth process $\dot{T}_B^2 = \mathcal{F}^2 = \kappa \alpha_B R G_B$ with 

@@

        The relation between inhibition strength of species $B$ and $A$ are defined by control parameter value (a) $\psi$ = 1, (b) $\psi$ = 0.5 or (c) $\psi$ = 2.

@@

        (a) $\psi=1, \phi=1$, (b) $\psi=1, \phi=2$ and (b) $\psi=2, \phi=1$.

@@

        (A) A cell right before and (B) after a division event.

@@

We see that in the highly-diffusive homogenous case of subfigure (a), the pool model is a good fit to the \ac{abm} model.
Heterogeneity and slower diffusion cause larger differences between the two models as can be seen in subfigures (b) and (c).

@@

In subfigure (c), due to the heterogeneous cell distribution (see Appendix~\ref{fig:supplement-spatial-initial-config-cells}), overall inhibition of species $B$ is significantly reduced.
Subfigure (d) shows how a randomized homogenous initial distribution can lead to even more notable effects of inhibition.

>>>>

% \documentclass[10pt,A4paper]{article}
\documentclass[10pt,twocolumn,5p,authoryear]{elsarticle}
\usepackage[utf8]{inputenc}

@@

\bibliographystyle{elsarticle-harv}

@@

        (\textbf{A}) The time dependence of the total bacterial count $N$ for the model including the back-flow to the lag phase due to temperature stress~(\ref{eq:ode_tempshift_backlag}).
        (\textbf{B}) The value of the corresponding back-flow rate $\gamma$ calculated according to (\ref{eq:gamma_tempshift}).

@@

        The growing bacteria $B$ produces toxin $T_B$ (\textbf{A}) constantly $\dot{T}_B^1 = \mathcal{F}^1 = \kappa G_B$ or (\textbf{B}) only during growth process $\dot{T}_B^2 = \mathcal{F}^2 = \kappa \alpha_B R G_B$ with

@@

        The relation between inhibition strength of species $B$ and $A$ are defined by control parameter value (\textbf{A}) $\psi$ = 1, (\textbf{B}) $\psi$ = 0.5 or (\textbf{C}) $\psi$ = 2.

@@

        (\textbf{A}) $\psi=1, \phi=1$, (\textbf{B}) $\psi=1, \phi=2$ and (\textbf{C}) $\psi=2, \phi=1$.

@@

        (\textbf{A}) A cell right before and (\textbf{B}) after a division event.

@@

We see that in the highly-diffusive homogenous case of subfigure (\textbf{A}), the pool model is a good fit to the \ac{abm} model.
Heterogeneity and slower diffusion cause larger differences between the two models as can be seen in subfigures (\textbf{B}) and \textbf{C}.

@@

In subfigure \textbf{C}, due to the heterogeneous cell distribution (see Appendix~\ref{fig:supplement-spatial-initial-config-cells}), overall inhibition of species $B$ is significantly reduced.
Subfigure (\textbf{D}) shows how a randomized homogenous initial distribution can lead to even more notable effects of inhibition.
